\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-17 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

From \eqref{ExplicitdPhidt}, it follows that $\frac{\differential}{\differential t}\Phi \leq 0$, i.e., $\Phi$ is non-increasing along the flow generated by \eqref{TransformedPDEivp}. Furthermore, \eqref{lastequality} tells us that $\frac{\differential}{\differential t}\Phi = 0$ if and only if 
$$\bm{M}^{-1}\bm{\Gamma}\bm{\eta} + \bm{\ell}_{\bm{\eta}} = 0$$

>>>>

From \eqref{ExplicitdPhidt}, it follows that $\frac{\differential}{\differential t}\Phi \leq 0$, i.e., $\Phi$ is non-increasing along the flow generated by \eqref{TransformedPDEivp}. Furthermore, \eqref{lastequality} tells us that $\frac{\differential}{\differential t}\Phi = 0$ if and only if 
$$\bm{M}^{-1}\bm{\Gamma}\bm{\eta} + \bm{\ell}_{\bm{\eta}} = 0,$$
i.e., when
